Fixing Vulnerabilities Hinders Maintainability

### 2019-02-04 paper/ICPC19/icpc19.tex

\setcounter{lstannotation}{0}
\begin{lstlisting}[style={PHPStyle}, caption={Fix provided by \texttt{nextcloud/server} developers to a \\Cross-Site Scripting vulnerability},label={lst:fix}]
 <ul>
   <li class='error'>
      <?php echo $l->t('Cloud not found');?><br/>
-     <p class='hint'><?php if(isset($_['file'])) echo $_['file']?></p>
+     <p class='hint'><?php if(isset($_['file'])) echo htmlentities($_['file'])?><?php 
   </li>
 </ul>

\end{lstlisting} \Luis{no listing lst:fix o que achas de fazer linebreak para
cada uma das tags? assim nao havi o problema de ter a mesma linha dividida e ficava mais facil de ler:\\
\texttt{<p class='hint'>}\\
\texttt{~~<?php }\\
\texttt{</p>}\\
Also: reduz numero de espacos para cada tab -- 2 é suficiente.
}
%
\section{Methodology}\label{sec:methodology}
%
The methodology used to measure the impact of security refactorings on the
maintainability of open-source software is discussed in this section. The
methodology is comprised of the following steps, as illustrated in
Figure~\ref{fig:met}\Luis{como usamos numeros na enumeracao que descreve a
figura, esses numeros tb deveriam estar na figura.}:

>>>>

\setcounter{lstannotation}{0}
\begin{lstlisting}[style={PHPStyle}, caption={Fix provided by \texttt{nextcloud/server} developers to a \\Cross-Site Scripting vulnerability},label={lst:fix}]
 <ul>
  <li class='error'>
   <?php echo $l->t('Cloud not found');?>
   <br/>
   <p class='hint'>
-    <?php if(isset($_['file'])) echo $_['file']?>
   </p>
   <p class='hint'>
+    <?php if(isset($_['file'])) echo htmlentities($_['file'])?>
   </p> 
  </li>
 </ul>

\end{lstlisting} % \Luis{no listing lst:fix o que achas de fazer linebreak para
% cada uma das tags? assim nao havi o problema de ter a mesma linha dividida e ficava mais facil de ler:\\
% \texttt{<p class='hint'>}\\
% \texttt{~~<?php }\\
% \texttt{</p>}\\
% Also: reduz numero de espacos para cada tab -- 2 é suficiente.
% }
%
\section{Methodology}\label{sec:methodology}
%
The methodology used to measure the impact of security refactorings on the
maintainability of open-source software is discussed in this section. The
methodology is comprised of the following steps, as illustrated in
Figure~\ref{fig:met}\Luis{como usamos numeros na enumeracao que descreve a
figura, esses numeros tb deveriam estar na figura.}:
